\mireval{}:\\ A Transparent Implementation of Common MIR Metrics

### 2014-07-11 paper/paper.tex
fixed affiliation numbering, back down to 6 pages

\author[1]{Colin Raffel}
\author[1,4]{Brian McFee}
\author[2]{Eric J. Humphrey}
\author[2,3]{Justin Salamon}
\author[2]{Oriol Nieto}
\author[1]{Dawen Liang}
\author[1]{Daniel P. W. Ellis}
\affil[1]{LabROSA, Dept.~of Electrical Engineering\\Columbia University, New York}
\affil[4]{Center for Jazz Studies\\Columbia University, New York}
\affil[2]{Music and Audio Research Lab\\New York University, New York}
\affil[3]{Center for Urban Science and Progress\\New York University, New York}

@@

\mireval{} is a Python library which currently includes metrics for the following tasks: Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction, and onset detection.
Each task is given its own submodule, and each metric is defined as a separate function in each submodule.
Each task submodule also includes common data pre-processing steps for the task.
Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
\mireval{} also includes a submodule \texttt{io} which provides convenience functions
for loading in task-specific data from common file formats (\eg{} comma/tab separated
    values, \texttt{.lab} files~\cite{harte2010towards}, \etc{}).
For readability, all code follows the PEP8 style guide\cite{van2001pep}.
\mireval{}'s only dependencies outside of the Python standard library are the free and open-source \texttt{SciPy}/\texttt{Numpy}\cite{jones2001scipy} and \texttt{scikit-learn}\cite{pedregosa2011scikit} Python libraries.

>>>>

\author[1]{Colin Raffel}
\author[1,2]{Brian McFee}
\author[3]{Eric J. Humphrey}
\author[3,4]{Justin Salamon}
\author[3]{Oriol Nieto}
\author[1]{Dawen Liang}
\author[1]{Daniel P. W. Ellis}
\affil[1]{LabROSA, Dept.~of Electrical Engineering\\Columbia University, New York}
\affil[2]{Center for Jazz Studies\\Columbia University, New York}
\affil[3]{Music and Audio Research Lab\\New York University, New York}
\affil[4]{Center for Urban Science and Progress\\New York University, New York}

@@

\mireval{} is a Python library which currently includes metrics for the following tasks: Beat detection, chord estimation, pattern discovery, structural segmentation, melody extraction, and onset detection.
Each task is given its own submodule, and each metric is defined as a separate function in each submodule.
Each task submodule also includes common data pre-processing steps for the task.
Every metric function includes detailed documentation, example usage, input validation, and references to the original paper which defined the metric.
\mireval{} also includes a submodule \texttt{io} which provides convenience functions
for loading in task-specific data from common file formats (\eg{} comma/tab separated
    values, \texttt{.lab} files~\cite{harte2010towards}, \etc{}).
For readability, all code follows the PEP8 style guide\cite{van2001pep}.
\mireval{}'s only dependencies outside of the Python standard library are the free and open-source \texttt{SciPy}/\texttt{Numpy}\cite{jones2001scipy} and \texttt{scikit-learn}\cite{pedregosa2011scikit} libraries.
